% My journal abbreviations -- version of 12 Oct 1994

\typeout{David's journal abbreviations - version of 2 May 2005.}

\def\AeEn{Aero.\ Eng.}
\def\CEP{Chem. Eng. Process.}
\def\MCM{Math. Comp. Modelling}
\def\JCompAM{J. Comp. App. Math.}
\def\JCompP{J. Comp. Physics}
\def\IEEENN{IEEE Trans. Neural Net.}
\def\AFM{Agri. Forest Met.}
\def\AAP{Astron.\ Astrophys.}
\def\ACP{Atmos.\ Chem.\ Phys.}
\def\AEn{Atmos.\ Environ.}
\def\AEna{Atmos.\ Environ.\ A}
\def\AG{Ann.\ Geophys.}
\def\AGahss{Ann.\ Geophys. - Atmos. Hydro. Space Sci.}
\def\AJ{Astron.\ J.}
\def\ANM{App. Num. Math.}
\def\AO{Appl. Opt.}
\def\AO{Atmos.\ Ocean}
\def\APJL{Astrophys.\ J.}
\def\APJS{Astrophys.\ J.\ (Supp.)}
\def\APJ{Astrophys.\ J.}
\def\AREPS{Ann.\ Rev.\ Earth Planet.\ Sci.}
\def\ASL{Atmos.\ Sci.\ Lett.}
\def\ASR{Advances in Space Res.}
\def\BAMS{Bull.\ Am.\ Meteorol.\ Soc.}
\def\BASUDCS{Bull.\ Acad.\ Sci.\ USSR Div.\ Chem.\ Sci.\ (Engl. Transl.)}
\def\BBPC{Ber.\ Bunsenges.\ Phys.\ Chem.}
\def\BCSJ{Bull.\ Chem.\ Soc.\ Jpn.}
\def\BLM{Boundary-Layer Met.}
\def\BSSA{Bull.\ Seismol.\ Soc.\ Am.}
\def\CJC{Canadian J.\ Chem.}
\def\CJRSB{Can.\ J.\ Res.\ Sect.\ B}
\def\CPC{Comp.\ Phys.\ Comm.}
\def\CPL{Chem.\ Phys.\ Lett.}
\def\CP{Chem.\ Phys.}
\def\EI{Environ.\ Int.}
\def\EOS{Eos Trans.\ AGU}
\def\EPSL{Earth Planet.\ Sci.\ Lett.}
\def\EP{Environ.\ Pollution}
\def\GCA{Geochim.\ Cosmochim.\ Acta}
\def\GJRAS{Geophys.\ J.\ R.\ Astron.\ Soc.}
\def\GRL{Geophys.\ Res.\ Lett.}
\def\GSAB{Geol.\ Soc.\ Am.\ Bull.}
\def\HSJ{Hydro.\ Sci.\ J.}
\def\IJCK{Int.\ J.\ Chem.\ Kinet.}
\def\IJEP{Int.\ J.\ Chem.\ Environ. \ Pollution}
\def\IJRS{Int.\ J.\ Remote Sens.}
\def\JAHS{J.\ Am.\  Helicopter\  Soc.}
\def\JAC{J.\ Atmos.\ Chem.}
\def\JACS{J.\ Am.\ Chem.\ Soc.}
\def\JAM{J.\ App.\ Met.}
\def\JAOT{J.\ Atmos. \ Ocean. \ Tech.}
\def\JASTP{J.\ Atmos.\ Sol.-Terr.\ Phys.}
\def\JAS{J.\ Atmos.\ Sci.}
\def\JATP{J.\ Atmos.\ Terr.\ Phys.}
\def\JC{J.\ Clim.}
\def\JCP{J.\ Chem.\ Phys.}
\def\JCSFT{J.\ Chem.\ Soc.\ Faraday Trans.}
\def\JGRa{J.\ Geophys.\ Res.\ (Atmos.)}
\def\JGR{J.\ Geophys.\ Res.}
\def\JMSJ{J.\ Met.\ Soc.\ Japan}
\def\JPCA{J.\ Phys.\ Chem. A}
\def\JPCRD{J.\ Phys.\ Chem.\ Ref.\ Data}
\def\JPC{J.\ Phys.\ Chem.}
\def\JPO{J.\ Phys.\ Oceanogr.}
\def\JPPA{J.\ Photochem.\ Photobiol.\ A-Chemistry}
\def\JPP{J.\ Photochem.\ Photobiol.}
\def\JQSRT{J.\ Quant.\ Spec.\ Rad.\ Trans.}
\def\MDAMPCE{Mem.\ Def.\ Acad., Math., Phys., Chem.\ Eng.\ (Yokosuka, Jpn.)}
\def\MNRAS{Mon.\ Not.\ R.\ Astron.\ Soc.}
\def\MWR{Mon.\ Weather Rev.}
\def\OMS{Organic Mass Spectrometry}
\def\PAG{Pure\ Appl.\ Geophys.}
\def\PASP{Publ.\ A.\ S.\ P.}
\def\PCCP{Phys.\ Chem.\ Chem.\ Phys.}
\def\PEPI{Phys.\ Earth Planet.\ Inter.}
\def\PRA{Phys.\ Rev.\ A}
\def\PRL{Phys.\ Rev.\ Lett.}
\def\PSS{Planet.\ Space Sci.}
\def\PSPOIE{Proc.\ Soc. Photo-Opt. Instr. Eng. ({SPIE})}
\def\QJRMS{Q.\ J.\ R.\ Meteorol.\ Soc.}
\def\QJ{Q.\ J.\ R.\ Meteorol.\ Soc.}
\def\QN{Quim. Nova}
\def\RG{Rev.\ Geophys.}
\def\NN{Neural Networks}
\def\NC{Neural Comp.}
\def\RS{Radio\ Sci.}
\def\RSE{Remote Sens. Environ.}
\def\SA{Sci. Am.}
\def\SICP{Symp.\ Int.\ Combust.\ Proc.}
\def\TELA{Tellus, Ser. A.}
\def\TELB{Tellus, Ser. B.}
\def\TEL{Tellus}
\def\Tel{Tellus}
\def\TFS{Trans.\ Faraday\ Soc.}
\def\TGARS{{IEEE} Trans.\ Geosci.\ Remote Sens.}
\def\TAES{{IEEE} Trans.\ Aero.\ Electronic\  Sys.}
\def\USGSOF{U.S.\ Geol.\ Surv.\ Open File Rep.}
\def\USGSPP{U.S.\ Geol.\ Surv.\ Prof.\ Pap.}
\def\PTRSa{Phil.\ Tran.\ R.\ Soc.\ London\ Series\ A-Math.\ Phys.\ Eng.\ Sci.}
